Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-08 proposal/proposal.tex
Small rename
Additions

\begin{abstract}
300 words or less. Also, we need to put the EECS department in the title area as our professional affiliation.
\end{abstract}

@@

\subsection{Introduction}
Introduction

@@

\section{Proposed Work}
\subsection{Automobile Detection}
Santiago
\subsection{Raspberry Pi Image Collection}
Kevin
\subsection{Central Basestation}
Everyone
\subsection{Server Processing}
Brandon
\subsection{Web Application}
Taylor

\section{Summary}
A summary \cite{johnson2012}

>>>>

\begin{abstract}
300 words or less. Talk about the motivation behind this project. Why it is important.
\end{abstract}

@@

\subsection{Introduction}
Introduction. Talk about the motivation behind this project. Why it is important.

@@

\section{Proposed Work}
\subsection{Automobile Detection}
The automobile detection subsystem provides a means for detecting ingress and egress of vehicles from a parking lot. This subsystem is to be placed on the side of the road next to each parking lot entrance and exit. Automobiles will be detected using a magnetometer which perceives the induced change in the local magnetic field as the metallic structure of the vehicle passes by as described in \cite{stillwell2013}. The automobile detection subsystem will be based around the commercially available Arduino Fio 16-bit  platform which utilizes the ubiquitous Atmel ATMEGA328p microcontroller.

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{autodetection}
\end{center}
\caption{Automobile Detection Subsystem Architecture}
\end{figure}

The hardware to be used for automobile detection will be contained in the same enclosure as the license plate image acquisition hardware.

The use of a magnetometer ensures that solely automobile and other large vehicles such as motorcycles are detected while pedestrians are ignored.

Work on the automobile detection subsystem will involve a variety of tests and analyses to ensure system and data integrity.

\subsection{License Plate Image Acquisition}
Kevin

\subsection{Central Basestation}
Everyone

\subsection{Server Processing}
Brandon

\subsection{Web Application}
Taylor

\subsection{Deployment}
Blah

\section{Summary}
A summary \cite{johnson2012} Talk about the motivation behind this project. Why it is important.
